Model of lens candidates from Space Warps CFHTLS

### 2016-06-24 paper2.tex
included new plots
editing examples section

\newcommand{\inclfig}[2]{
  \centering
	\includegraphics[width=0.5\linewidth]{spaghetti/#2_input}%
	\includegraphics[width=0.5\linewidth]{spaghetti/#2_img1}
	\includegraphics[width=0.5\linewidth]{spaghetti/#2_img3_ipol}%
	\includegraphics[width=0.5\linewidth]{spaghetti/#2_img2}
	\includegraphics[width=\linewidth]{masses/#1_#2_mstel_vs_mtot}
}

@@

\section{Example systems}

\begin{figure}
  \inclfig{SW02}{ASW000619d_011489}
  \caption{SW02}
  \label{fig:SW02}
\end{figure}

\begin{figure}
  \inclfig{SW05}{ASW0007k4r_AJIBCHQ6EM}
  \caption{SW05}
  \label{fig:SW05}
\end{figure}

\begin{figure}
  \inclfig{SW09}{ASW0002asp_5EKMWWVJHL}
  \caption{SW09}
  \label{fig:SW09}
\end{figure}

\begin{figure}
  \inclfig{SW28}{ASW0007xrs_JHC3J2HYV7}
  \caption{SW28}
  \label{fig:SW28}
\end{figure}

\begin{figure}
  \inclfig{SW29}{ASW0008qsm_TOFS7JNGEK}
  \caption{SW29}
  \label{fig:SW29}
\end{figure}

@@

\begin{figure}
  \inclfig{SW58}{ASW0007iwp_4XBJWT3COV}
  \caption{SW58. topleft: user input; top right: resulting contour map of arrival time surface; mid left: synthetic image, renering a TODO{profile} source behind the modelled lens; mid right: mass profile; bottom: lensing mass, obtained from the model against estimate of stellar mass, obtained using photometric redshift assuming TODO(which population model?).}
  \label{fig:SW58}
\end{figure}

@@

\begin{figure}
  \inclfig{SW36}{ASW000096t_7IPP7LWVOF}
\end{figure}

\begin{figure}
  \inclfig{SW19}{ASW0001ld7_OS3CYAKLRT}
\end{figure}

\begin{figure}
  \inclfig{SW57}{ASW0008pag_5SXGXQYY6V}
\end{figure}

@@

\begin{figure}
  \inclfig{SW42}{ASW00096rm_4Q3YCEWGLN}
  \caption{outlier because very odd mass ratio}
  \label{fig:SW42}
\end{figure}

@@

\todo{REMOVE TODOS at the end}

>>>>

\edef\smallwidth{0.4\linewidth}

\newcommand{\inclfig}[2]{
  \centering
	\includegraphics[width=\smallwidth]{spaghetti/#2_input}%
	\includegraphics[width=\smallwidth]{spaghetti/#2_img2}
	\includegraphics[width=\smallwidth]{spaghetti/#2_img1}%
	\includegraphics[width=\smallwidth]{img/M_encl/#2_M_encl}
	\includegraphics[width=\smallwidth]{spaghetti/#2_img3_ipol}%
	\includegraphics[width=\smallwidth]{masses/#1_#2_mstel_vs_mtot}
}

\newcommand{\inclfign}[2]{
  \centering
	\includegraphics[width=\smallwidth]{spaghetti/#2_input}%
	\includegraphics[width=\smallwidth]{spaghetti/#2_img2}
	\includegraphics[width=\smallwidth]{spaghetti/#2_img1}%
	\includegraphics[width=\smallwidth]{img/M_encl/#2_M_encl}
	\includegraphics[width=\smallwidth]{img/nsynth/#2_nsynth}%
	\includegraphics[width=\smallwidth]{masses/#1_#2_mstel_vs_mtot}
}

@@

\section{Example systems}\label{sec:examples}

. topleft: user input; top right: resulting contour map of arrival
time surface; mid left: synthetic image, renering a conical profile
source behind the modelled lens; mid right: mass profile\todo{Fix
  distance factor in $\kappa$.}  ; bottom: lensing mass, obtained from
the model against estimate of stellar mass, obtained using photometric
redshift assuming \todo{which population model?}

\begin{figure}
  \inclfign{SW28}{ASW0007xrs_JHC3J2HYV7}
  \caption{SW28.  See text in Section~\ref{sec:examples} for details.}
  \label{fig:SW28}
\end{figure}

\begin{figure}
  \inclfign{SW05}{ASW0007k4r_AJIBCHQ6EM}
  \caption{SW05}
  \label{fig:SW05}
\end{figure}

\begin{figure}
  \inclfign{SW02}{ASW000619d_011489}
  \caption{SW02}
  \label{fig:SW02}
\end{figure}

\begin{figure}
  \inclfign{SW09}{ASW0002asp_5EKMWWVJHL}
  \caption{SW09}
  \label{fig:SW09}
\end{figure}

\begin{figure}
  \inclfign{SW29}{ASW0008qsm_TOFS7JNGEK}
  \caption{SW29}
  \label{fig:SW29}
\end{figure}

@@

\begin{figure}
  \inclfig{SW58}{ASW0007iwp_4XBJWT3COV}
  \caption{SW58}
  \label{fig:SW58}
\end{figure}

@@

\begin{figure}
  \inclfig{SW36}{ASW000096t_7IPP7LWVOF}
  \caption{}
  \label{fig:SW36}
\end{figure}

\begin{figure}
  \inclfig{SW19}{ASW0001ld7_OS3CYAKLRT}
  \caption{}
  \label{fig:SW19}
\end{figure}

\begin{figure}
  \inclfig{SW57}{ASW0008pag_5SXGXQYY6V}
  \caption{}
  \label{fig:SW57}
\end{figure}

@@

\begin{figure}
  \inclfig{SW42}{ASW00096rm_4Q3YCEWGLN}
  \caption{Models of SW42, a doubtful candidate because of an
    implausible mass ratio. (See text for details.)}
  \label{fig:SW42}
\end{figure}

@@
